Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
sections 2-3

\textbf{Discretization Effects --}
The classical approach to control synthesis has often disregarded
digitalization effects, whereas more recently modern techniques have focused
on different aspects of discretization, including delayed
response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
the goal either to verify~\cite{daes20161} or to
optimize~\cite{oudjida2014design} given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding and
saturation errors during computation.  In~\cite{fialho1994stability}, a
stability measure based on the error of the digital dynamics ensures that
the deviation introduced by FWL does not make the digital system unstable. 
A~more recent approach~\cite{DBLP:journals/automatica/WuLCC09} uses
$\mu$-calculus to directly model the digital controller so that the selected
parameters are stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses bounded-input and bounded-output
(BIBO) properties to determine stability, the latter uses Lyapunov-based
quadratic invariants.  In both cases, the SDP solver uses floating-point
arithmetic and soundness is checked by bounding the error.  An alternative
is~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code by
symbolic execution: to account for rounding errors, an upper bound is
introduced in the verification phase.  The work
in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  Similarly,
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and
bounds its trajectory to a known region over a finite time period.  This
technique works for both linear and non-linear systems.

@@

Equation~\eqref{eq:ode1} is soundly discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
of duration $T_s$ (the sample time), 
into the difference equation
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
\end{align} 
where 
$\mat{A}_d=e^{\mat{A}T_s}$ and 
$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
and where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.

Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the plant.   
We are interested in the synthesis of digital feedback control algorithms, 
as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
Later, we will address the issue of variable quantization, 
introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
as classically studied in \cite{astrom1997computer}.

@@

We account for the presence of errors originating from a number of sources, shown in Figure~\ref{}:
\begin{itemize}
\item We represent the plant variables $x(t)$ and $u(t)$, which are real numbers, at a finite precision in our model, and so it is necessary to account for the errors introduced by this representation. We account for these errors in both back ends by using interval arithmetic, detailed in section~\ref{}. 
\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into
the digital signal $x_k$ which is fed into the controller. We account for this error in 
the acceleration based back-end by introducing a noise signal $\nu_1$ that over-approximates this error, 
shown in the figure. Further details are found in section~\ref{}. 
In the naive back end we use bit-precise modelling in CBMC~\cite{} to accurately model this deterministic
conversion. In other words, CBMC constructs a boolean formula which explicitly unwinds the transition system for any symbolically represented input state, bounded by the initial conditions, and performs the ADC conversion precisely on that symbolically represented input state. When we verify safety, the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property. 
\item The representation errors due to performing finite-precision arithmetic in the controller. 
In the acceleration based back-end, this is again treated by the introduction of noise that bounds the error.
The naive back end uses the bit-precise modelling of finite-precision arithmetic in CBMC, in the same way as we handled the ADC conversion. We assume that the controller
represents numbers to the same precision as the ADC.
\item We assume that the DAC converts numbers from the same precision as the controller to an analogue signal. 
As a result we can ignore any errors introduced by the DAC
\end{itemize}

>>>>

\textbf{Discretization Effects --}
Classical work in control synthesis has often disregarded digitalization effects, 
\note{[this paragraph needs more work:]
whereas recent results in digital control have focused on separate aspects of discretization, 
including delayed response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
with the goal either to verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} given implementations. }

There are two different problems that arise from FWL semantics.  The first
is the error in the model dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding and
saturation errors during model manipulation.  
In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
the deviation introduced by FWL does not lead to instability.  
\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to directly model the digital controller so that selected
parameters result by design in stable dynamics.  
The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete dynamics using Semi-Definite
Programming (SDP):  while the former contribution uses bounded-input and bounded-output
(BIBO) properties to determine stability, the latter uses Lyapunov-based
quadratic invariants.  In both cases, the SDP solver uses floating-point
arithmetic and soundness is checked by bounding the error.  
An alternative is~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code by
symbolic execution: to account for rounding errors, an upper bound is
introduced in the verification phase.  
The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
bound the quantization error effect on stabilization.  
% as an invariant set that always converges toward the controllable set.  
Similarly, 
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and \note{[unclear] bounds its trajectory to a known region over a finite time period}.   
%This technique works for both linear and non-linear systems.

@@

Equation~\eqref{eq:ode1} is 
%soundly 
discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
of duration $T_s$ (the sample time), 
into the difference equation
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
\end{align} 
where 
$\mat{A}_d=e^{\mat{A}T_s}$ and 
$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.

Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the plant:    
we are interested in the synthesis of digital feedback controllers $u_k$,  
as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
\note{next: why only this single issue, rather than all discretisation effects as presented earlier?} Later, we will address the issue of variable quantization, 
introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
as classically studied in \cite{astrom1997computer}.

@@

\note{back end vs back-end?}

We account for the presence of errors originating from a number of sources, shown in Figure~\ref{} \note{fix}:
\begin{itemize}
\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
It is necessary to account for the errors introduced by this representation: 
we account for these errors in both back ends \note{did we explain the two back ends already?} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
which is then fed into the controller \note{cf. Figure~\ref{} }. 
We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{}.  
In the naive back-end we use bit-precise modelling in \note{[clear? discussed before?] CBMC}~\cite{} to accurately encompass this conversion.   
In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for any \note{[unclear] symbolically represented} input state, 
\note{[unclear how the initial conditions bound the input state? use formulas or figure to explain.] bounded by the initial conditions}, 
and performs the ADC conversion precisely on that symbolically represented input state. 
When we check for a safety property, 
the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.  
\item The representation errors due to performing finite-precision arithmetic in the controller block. 
In the acceleration-based back-end, 
this is again treated by the introduction of a noise signal that bounds the error. 
The naive back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
in the same way as we handled the ADC conversion. 
We assume that the controller represents numbers to the same precision as the ADC \note{why is this legit?}. 
\item We assume \note{why is this reasonable?} that the DAC converts numbers to analogue signals with the same precision as the controller. 
As a result we can ignore any additional errors introduced by the DAC.  
\end{itemize}
